Recursive algorithms, branching coefficients and applications

### 2010-10-31 AffineLieAlgebras/InformalNotes/article.tex
Section 2 is rewritten, theorem added.

\newtheorem{statement}{Statement}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{corollary}{Corollary}[theorem]
\theoremstyle{definition}
\newtheorem{mynote}{Note}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}

@@

 $k_{\lambda}$ --- the anomalous branching coefficients, notice that
\begin{equation*}
%  \label{eq:20}
  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}};
\end{equation*}

@@

\section{Recurrent relation for branching coefficients. Singularities and subtractions}
\label{sec:recurr-form-branch}

We consider an injection of affine Lie algebras $\frak{a}\longrightarrow \frak{g%
}$ such that $\frak{a}$ is a reductive subalgebra $\frak{a\subset g}$.
In this section we deduce the general recurrent relation (\ref{eq:1}) for the anomalous branching coefficients (\ref{eq:21}). This relation is then used to formulate the practical computational algorithm (Subsection \ref{sec:algorithm}).
In the earlier paper \cite{ilyin812pbc} the following limited setup was considered: $\mathfrak{a}$ was required to be the maximal subalgebra of $\mathfrak{g}$ so that no zeros arrive in the Weyl denominator $R$. Here we raise this limitation and study the general case $\mathfrak{a}\subset\mathfrak{g}$.

\subsection{Some definitions}
\label{sec:some-definitions}

We need to introduce several additional definitions and state some technical results to formulate and prove the recurrent relation (\ref{eq:1}).

\begin{definition}
  Denote by $\Delta^{+}_{\bot}=\left\{\alpha\in \Delta^{+}_{\mathfrak{g}}:\forall \beta\in\Delta_{\mathfrak{a}} \; \alpha\bot \beta\right\}$ the subset of the positive roots of $\mathfrak{g}$ orthogonal to the root system of $\mathfrak{a}$.
\end{definition}

\begin{definition}
  Denote by $W_{\bot}$ the subgroup of the Weyl group $W$ generated by the reflections $\omega_{\alpha}$ corresponding to the roots $\alpha\in \Delta^{+}_{\bot}$.
\end{definition}
\begin{mynote}
  The subgroup $W_{\bot}$ preserves $\Delta_{\mathfrak{a}}$ since it is generated by the reflections in hyperplanes containing $\Delta_{\mathfrak{a}}$.
\end{mynote}
\begin{definition}
  The subsystem $\Delta_{\bot}=\Delta^{+}_{\bot}\cup \left(-\delta^{+}_{\bot}\right)$ determines the subalgebra $\mathfrak{a}_{\bot}\subset \mathfrak{g}$.
\end{definition}

We need to know when the subset $\Delta^{+}_{\bot}$ is non-empty and $W_{\bot},\mathfrak{a}_{\bot}$ are non-trivial. So we state several simple lemmas.

For the simple finite-dimensional Lie algebras $\ao,\go$ all the regular embeddings can be obtained by the successive elimination of the nodes in the extended Dynkin diagram of $\go$. This leads to the lemma
\begin{lemma}
  For the regular embedding $\ao\subset \go$ 
  \renewcommand{\theenumi}{\alph{enumi}}
  \begin{enumerate}
  \item $\Delta^{+}_{\bot}=\emptyset$ if $\ao$ is maximal
  \item If the extended Dynkin diagram of $\go$ contains the disconnected subdiagrams of $\ao$ and some subalgebras $\left\{\co{\mathfrak{a}_j}\right\}$ then $\Delta^{+}_{\bot}\neq \emptyset$ and $\co{\mathfrak{a}_j}\subset \mathfrak{a}_{\bot}$.
  \end{enumerate}
\end{lemma}
\begin{mynote}
  The complete classification of the regular subalgebras for affine Lie algebras can be
  found in the recent paper \cite{1751-8121-41-36-365204}.
\end{mynote}
\begin{mynote}
  $\mathfrak{a}_{\bot}$ may be larger than the algebra $\bigoplus_j \co{\mathfrak{a}_j}$.
\end{mynote}
Consider for example the embedding of $B_2\subset B_4$ (the Figure \ref{fig:dynkin}).
In this case by eliminating
the simple root $\alpha_2=e_2-e_3$ one splits the extended Dynkin diagram of $B_4$
into the diagrams of the subalgebra $\mathfrak{a}=B_2$ and that of the direct
sum $A_1 \oplus A_1 $. But the subalgebra $\mathfrak{a}_{\bot}$ is equal to $B_2$
(the root system of $B_4$ contains not only $\alpha_2=e_2-e_3$ but also $e_2$).

Such effects are due to the fact that the subalgebras $\mathfrak{a}$ and $\mathfrak{a}_{\bot}$
must not form a direct sum in $\mathfrak{g}$.
Consider the case of such a regular embedding $\mathfrak{a}\subset \mathfrak{g}$ where both
algebras are simple and the diagram of the subalgebra $\mathfrak{a}_{\bot}$ is not a
subdiagram of the extended Dynkin diagram $\mathfrak{g}$.
Drop the subdiagram of $\mathfrak{a}$ and the node $\alpha'$ that connects it with
the remaining nodes of the diagram of $\mathfrak{g}$. The result is the diagram of
the algebra $\bar{\mathfrak{a}}$ with $\mathrm{rank}(\bar{\mathfrak{a}}) =
\mathrm{rank}(\mathfrak{g})-\mathrm{rank}(\mathfrak{a})$. It is clear that
$\bar{\mathfrak{a}}\subset \mathfrak{a}_{\bot}$. So the question is whether
$\mathfrak{a}_{\bot}$ has additional roots,  not the roots of $\bar{\mathfrak{a}}$
but the linear combinations of them. The answer is positive  when the set of angles
between the roots of $\bar{\mathfrak{a}}$ does not contain all the angles between
the roots of $\mathfrak{a}$.
Then by reflecting the roots of $\mathfrak{a}$ by $s_{\alpha'}$ we get the additional
roots of $\mathfrak{a}_{\bot}$.
Case-by-case analysis illustrated by the table \ref{tab:diagrams} leads us to the following lemma.

\begin{table}[h!tb]
\label{tab:diagrams}
\noindent  \centering{
\begin{tabular}{|l|l|l|l|}
  \hline
  $\mathfrak{g}$ & Extended diagram of $\mathfrak{g}$ &
  Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
  \hline
  $A_n$ & \includegraphics{table1_1(l).eps} & \includegraphics{table1_1(r).eps} \\
  \hline
  $B_n$ & \includegraphics{table1_2(l).eps} & \includegraphics{table1_2(r).eps} \\
  \hline
  $C_n$ & \includegraphics{table1_3(l).eps} & \includegraphics{table1_3(r).eps} \\
  \hline
  $D_n$ & \includegraphics{table1_4(l).eps} & \includegraphics{table1_4(r).eps} \\
  \hline
\end{tabular}
\caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
\end{table}

\begin{lemma}
  \renewcommand{\theenumi}{\alph{enumi}}
  \begin{enumerate}
  \item If $\go,\ao\neq B_r$ the Dynkin diagram of $\mathfrak{a}_{\bot}$ is obtained from the extended Dynkin diagram of $\go$ by dropping the subdiagram of $\ao$ and the adjacent nodes
  \item If $\go=B_r$ and $\ao=B_{r_{\mathfrak{a}}}$ then $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
  \end{enumerate}
\end{lemma}
The complete classification of maximal special subalgebras in classical Lie algebras
\cite{dynkin1952semisimple} allows us to formulate
\begin{lemma}
  For the special embeddings there exist the following set of pairs of orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$:
\begin{equation*}
%  \label{eq:42}
  \begin{array}{lll}
      su(p)\oplus su(q) & \subset su(pq) &\\
      so(p)\oplus so(q) & \subset so(pq) &\\
      sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
      sp(2p)\oplus so(q) & \subset sp(2pq)&\\
      so(p)\oplus so(q) & \subset so(p+q)& \mbox{for}\;p\;\mbox{and}\;q\;\mbox{odd}.\\
  \end{array}
\end{equation*}
\end{lemma}
We are almost ready to state and prove the recurrent relation for the anomalous branching coefficients.
\begin{definition}
  \label{fan-definition}
  For affine $\mathfrak{a}\subset\mathfrak{g}$ expand the product
  \begin{equation*}
    \label{eq:6}
    \prod_{\alpha\in \Delta^{+}\setminus\Delta^{+}_{\bot}}
    \left(1-e^{-\pi_{\mathfrak{a}}\alpha}\right)^{
        \mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\pi_{\mathfrak{a}}\alpha)}=
      -\sum_{\gamma\in P_{\mathfrak{a}}}e^{-\gamma}
  \end{equation*}
  Denote by $\Phi_{\mathfrak{a}\subset\mathfrak{g}}\subset P_{\mathfrak{a}}$ the carrier of the coefficient function $s(\gamma)$. 
  \begin{equation*}
    \label{eq:37}
    \Phi_{\mathfrak{a}\subset\mathfrak{g}}=\left\{\gamma\in P_{\mathfrak{a}}|s(\gamma)\neq 0\right\}
  \end{equation*}

  The ordering of roots in $\co{\Delta_{\mathfrak{a}}}$ induce the natural ordering on the weights of $\mathfrak{a}$. Denote by $\gamma_0$ the lowest vector of $    \Phi_{\mathfrak{a}\subset\mathfrak{g}}$ according to this ordering. 
  The set 
  \begin{equation}
    \Gamma _{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
        \frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
    \label{fan-defined}
  \end{equation}
  is called the {\it injection fan}.
\end{definition}

\subsection{Proof of the recurrent relation}
\label{sec:proof}
\begin{theorem}
  For the anomalous branching coefficients (\ref{eq:21}) holds the recurrent relation
  \begin{equation}
    \label{eq:1}
    \label{recurrent-relation}
    \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
        \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\;
        {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)
        \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+ \right.\\
      \left.
        +\sum_{\gamma \in
          \Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
          +\gamma }^{\left( \mu \right) }\right).
    \end{array}
  \end{equation}
  \begin{proof}
    Consider the branching of a module $L_{\frak{g}}^{\mu }$ in terms of formal characters and
    projection operators $\pi_{\mathfrak{a}}:P\to P_{\mathfrak{a}}$:
    \begin{equation*}
      % \label{eq:3}
      L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
        }^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }\quad
      \Longrightarrow\quad
      \pi_{\mathfrak{a}}(ch L^{\mu}_{\mathfrak{g}})=
      \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu} ch L^{\nu}_{\mathfrak{a}}.
    \end{equation*}
    The Weyl-Kac character formula leads to
    the relation
    \begin{equation}
      \label{eq:4}
      \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}
        {\prod_{\alpha\in\Delta^{+}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) =
      \sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
      \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)
        e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}
      {\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
    \end{equation}

    Consider the direct sum $\mathfrak{a}_{\bot}\oplus\mathfrak{h}_{\mathfrak{a}}$ and
    its module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
    with the highest weight $\mu$. The character $ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$
    can be written as
    \begin{equation*}
      % \label{eq:41}
      ch L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}=
      \frac{\sum_{\omega\in W_{\bot}} \epsilon(\omega)
        e^{\omega(\mu+\rho_{\mathfrak{a}_{\bot}})-\rho_{\mathfrak{a}_{\bot}}}}
      {\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}.
    \end{equation*}
    Its projection $\pi_{\mathfrak{a}}(ch\, L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}})$
    is the element $e^{\pi_{\mathfrak{a}} \cdot\mu}$ of the formal algebra ${\cal E}\left( \mathfrak{a}\right)$
    with the multiplicity equal to the dimension of the module $L^{\mu}_{\mathfrak{a}_{\bot}\oplus \mathfrak{h}}$,
    since all the roots of $\mathfrak{a}_{\bot}$ are orthogonal to  that of $\Delta_{\mathfrak{a}}$.

    Using this property we can consider the restriction
    $ch\, L^{\mu}_{\mathfrak{g}\downarrow \mathfrak{a}_{\bot}\oplus \mathfrak{h}}$,
    that is the character of the direct sum of $\left( \mathfrak{a}_{\bot}\oplus\mathfrak{h}\right) $-modules.
    Multiply the equation (\ref{eq:4}) by the element
    \begin{equation*}
      % \label{eq:5}
      \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}
        (1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)
    \end{equation*}
    and take into account that the projection commutes with the multiplication:
    \begin{eqnarray*}
      \label{eq:7}
      \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
      \pi_{\mathfrak{a}}\left(\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}_{\mathfrak{g}}(\alpha)} \right)\sum_{\nu\in P^{+}_{\mathfrak{a}}}b^{(\mu)}_{\nu}
      \frac{\sum_{\omega\in W_{\mathfrak{a}}}\epsilon(\omega)e^{\omega(\nu+\rho_{\mathfrak{a}})-\rho_{\mathfrak{a}}}}{\prod_{\beta\in \Delta_{\mathfrak{a}}^{+}}(1-e^{-\beta})^{\mathrm{mult}_{\mathfrak{a}}(\beta)}}.
    \end{eqnarray*}
    Rewriting this relation in terms of the anomalous branching coefficients (\ref{eq:21}) and simplifying the first factor we get
    \begin{eqnarray*}
      \label{eq:12}
      \pi_{\mathfrak{a}}\left(\frac{\sum_{\omega\in W} \epsilon(\omega) e^{\omega(\mu+\rho)-\rho}}{\prod_{\alpha\in\Delta^{+}_{\bot}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)}}\right) = \\
      \left(\prod_{\alpha\in \pi_{\mathfrak{a}}\left(\Delta^{+}\setminus \Delta^{+}_{\bot}\right)}(1-e^{-\alpha})^{{\rm mult}_{\mathfrak{g}}(\alpha)-{\rm mult}_{\mathfrak{a}}(\alpha)} \right)
      \sum_{\lambda \in P_{\frak{a}}}k_{\lambda}^{\left( \mu \right) }e^{\lambda }.
    \end{eqnarray*}

>>>>

\newtheorem{statement}{Statement}
\theoremstyle{definition}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{corollary}{Corollary}[theorem]
\theoremstyle{definition}
\newtheorem{mynote}{Note}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}[theorem]{Remark}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}

@@

 $k_{\lambda}$ --- the anomalous branching coefficients, notice that
\begin{equation}
%  \label{eq:20}
  b^{(\mu)}_{\nu}=k^{(\mu)}_{\nu} \; \mbox{for} \; \nu\in \bar{C}_{\mathfrak{a}};
\label{eq:21-1}
\end{equation}

@@

\section{Recurrent relation for branching coefficients.}
\label{sec:recurr-form-branch}

Let $\frak{a}\subset \frak{g}$ be a regular subalgebra of $\frak{g.}$
Applying the Weyl-Kac character formula to the branching rule $\pi _{\frak{a}%
}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu
)}ch\left( L_{\frak{a}}^{\nu }\right) $ we get the relation connecting the
singular elements $\Psi ^{\left( \mu \right) }$ and $\Psi _{\left( \frak{a}%
\right) }^{\left( \nu \right) }$ :
\begin{eqnarray}
\pi _{\frak{a}}\left( \frac{\sum_{\omega \in W}\epsilon (\omega )e^{\omega
(\mu +\rho )-\rho }}{\prod_{\alpha \in \Delta ^{+}}(1-e^{-\alpha })^{\mathrm{%
mult}(\alpha )}}\right) &=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}%
\frac{\sum_{\omega \in W_{\frak{a}}}\epsilon (\omega )e^{\omega (\nu +\rho _{%
\frak{a}})-\rho _{\frak{a}}}}{\prod_{\beta \in \Delta _{\frak{a}%
}^{+}}(1-e^{-\beta })^{\mathrm{mult}_{\frak{a}}(\beta )}},  \label{eq:4} \\
\pi _{\frak{a}}\left( \frac{\Psi ^{\left( \mu \right) }}{R}\right)
&=&\sum_{\nu \in P_{\frak{a}}^{+}}b_{\nu }^{(\mu )}\frac{\Psi _{\left( \frak{%
a}\right) }^{\left( \nu \right) }}{R_{\frak{a}}}.
\end{eqnarray}
where according to our notations $\Delta _{\frak{a}}^{+}$ is the set of
positive roots of the subalgebra $\frak{a}$ (it is convenient to choose them
from the positive root subspace of $\frak{g}$). Consider the root space $%
\frak{h}_{\perp \frak{a}}^{\ast }$ orthogonal to $\Delta _{\frak{a}}$,
\begin{equation*}
\frak{h}_{\perp \frak{a}}^{\ast }=:\left\{ \eta \in \frak{h}_{\frak{g}%
}^{\ast }|\forall \alpha \in \Delta _{\frak{a}};\alpha \bot \eta \right\} ,
\end{equation*}
and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
to $\Delta _{\frak{a}}$,
\begin{eqnarray*}
\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
\alpha \in \Delta _{\frak{a}};\alpha \bot \beta \right\} , \\
\Delta _{\frak{a}_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
}^{+}|\forall \alpha ^{+}\in \Delta _{\frak{a}}^{+};\alpha ^{+}\bot \beta
^{+}\right\} .
\end{eqnarray*}
Let $W_{\frak{a}_{\perp }}$ be the subgroup of $W$ generated by the
reflections $\omega _{\beta }$ for the roots $\beta \in \Delta _{\frak{a}%
_{\perp }}^{+}$ . The subsystem $\Delta _{\frak{a}_{\perp }}$ determines the
subalgebra $\frak{a}_{\perp }$ with the Cartan subalgebra $\frak{h}_{\frak{a}%
_{\perp }}$. Let
\begin{equation*}
\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \frak{a}}^{\ast
}|\forall \alpha \in \Delta _{\frak{a}}\cup \Delta _{\frak{a}_{\perp
}};\alpha \bot \eta \right\}
\end{equation*}
and consider the subalgebras
\begin{eqnarray*}
\widetilde{\frak{a}_{\perp }} &:&=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
\\
\widetilde{\frak{a}} &:&=\frak{a}\oplus \frak{h}_{\perp }.
\end{eqnarray*}

The algebras $\frak{a}$ and $\frak{a}_{\perp }$ form an ''orthogonal pair''
of subalgebras in $\frak{g}$. For the Cartan subalgebras we have the
decomposition
\begin{equation}
\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus
\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\frak{a}}}}\oplus \frak{h}_{%
\frak{a}_{\perp }}=\frak{\frak{h}_{\widetilde{\frak{a}_{\perp }}}}\oplus
\frak{h}_{\frak{a}}.
\end{equation}
For the subalgebras of the orthogonal pair $\left( \frak{a},\frak{a}_{\perp
}\right) $ we consider the corresponding Weyl vectors, $\rho _{\frak{a}}$
and $\rho _{\frak{a}_{\perp }}$ , and\ form the so called ''defects'' $%
\mathcal{D}_{\frak{a}}$ and $\mathcal{D}_{\frak{a}_{\perp }}$ of the
injection:
\begin{equation}
\mathcal{D}_{\frak{a}}:=\rho _{\frak{a}}-\pi _{\frak{a}}\rho ,
\end{equation}
\begin{equation}
\mathcal{D}_{\frak{a}_{\perp }}:=\rho _{\frak{a}_{\perp }}-\pi _{\frak{a}%
_{\perp }}\rho .
\end{equation}
For the highest weight module $L_{\frak{g}}^{\mu }$ consider the singular
weights $\left( w(\mu +\rho )-\rho \right) \in \widehat{\Psi ^{\left( \mu
\right) }}$ and their projections to $h_{\widetilde{\frak{a}_{\perp }}%
}^{\ast }$ (additionally shifted by $-\mathcal{D}_{\frak{a}_{\perp }}$):
\begin{equation*}
\mu _{\widetilde{\frak{a}_{\perp }}}\left( w\right) :=\pi _{\widetilde{\frak{%
a}_{\perp }}}\left[ w(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp
}},\quad w\in W.
\end{equation*}
Among the weights $\mu _{\widetilde{\frak{a}_{\perp }}}\left( w\right)
|_{w\in W}$ choose those located in the fundamental chamber $\overline{C_{%
\widetilde{\frak{a}_{\perp }}}}$ and let $U$ be the set of representatives $%
u $ for the classes $W/W_{\frak{a}_{\perp }}$ such that

\begin{equation}
U:=\left\{ u\in W|\quad \mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right)
\in \overline{C_{\widetilde{\frak{a}_{\perp }}}}\right\} \quad .
\label{U-def}
\end{equation}
For the same set $U$ introduce the weights
\begin{equation*}
\mu _{\frak{a}}\left( u\right) :=\pi _{\frak{a}}\left[ u(\mu +\rho )-\rho %
\right] +\mathcal{D}_{\frak{a}_{\perp }}.
\end{equation*}

To describe the recurrent properties for branching coefficients $b_{\nu
}^{(\mu )}$ we shall use the technique elaborated in \cite{ilyin812pbc} one of the
main tools of which is the set of weights $\Gamma _{\frak{a}\subset \frak{g}%
} $ called the injection fan. As far as we consider more general situation
(where the injection is not maximal) the notion of the injection fan is
modified:

\begin{definition}
\label{fan-definition} For the product
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
_{\frak{a}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\frak{a}%
}(\pi _{\frak{a}}\alpha )}=-\sum_{\gamma \in P_{\frak{a}}}s(\gamma
)e^{-\gamma }  \label{eq:6}
\end{equation}
consider the carrier $\Phi _{\frak{a}\subset \frak{g}}\subset P_{\frak{a}}$
of the function $s(\gamma )=\det \left( \gamma \right) $ :
\begin{equation}
\Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}|s(\gamma
)\neq 0\right\}   \label{eq:37}
\end{equation}
The ordering of roots in $\co{\Delta _{\frak{a}}}$ induce the
natural ordering of the weights in $P_{\frak{a}}$. Denote by $\gamma _{0}$
the lowest vector of $\Phi _{\frak{a}\subset \frak{g}}$ . The set
\begin{equation}
\Gamma _{\frak{a}\subset \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
\frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
\label{fan-defined}
\end{equation}
is called the \textit{injection fan}.
\end{definition}

The main result is that the Weyl-Kac character formula (in terms of singular
elements) describes the particular case of a more general relation:

\begin{lemma}
Let $\frak{a}$ and $\frak{a}_{\perp }$ be the orthogonal pair of regular
subalgebras in $\frak{g}$, with $\widetilde{\frak{a}_{\perp }}=\frak{a}%
_{\perp }\oplus \frak{h}_{\perp }$ and $\widetilde{\frak{a}}=\frak{a}\oplus
\frak{h}_{\perp }$ ,

$L_{\frak{g}}^{\mu }$ be the highest weight module with the singular element
$\Psi _{\frak{g}}^{\mu }$ ,

$R_{\frak{a}_{\perp }}$ be the Weyl denominator for $\frak{a}_{\perp }$.

Then the element $\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{%
\frak{a}_{\perp }}}\right) $ can be decomposed into the sum over $u\in U$ (see (\ref{U-def})) of
the singular elements $e^{\mu _{\frak{a}}\left( u\right) }$ with the
coefficients $\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\frak{a}_{\perp
}}}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) }\right) $:
\begin{equation}
\quad \pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\frak{a}%
_{\perp }}}\right) =\sum_{u\in U}\;\epsilon (u)e^{\mu _{\frak{a}}\left(
u\right) }\mathrm{\dim }\left( L_{\widetilde{\frak{a}_{\perp }}}^{\mu _{%
\widetilde{\frak{a}_{\perp }}}\left( u\right) }\right) .
\end{equation}
\end{lemma}

\begin{proof}
For $u\in $ $U$ \ perform the following decompositions:
\begin{equation*}
u(\mu +\rho )=\pi _{\left( \frak{a}\right) }u(\mu +\rho )+\pi _{\left(
\widetilde{\frak{a}_{\perp }}\right) }u(\mu +\rho )
\end{equation*}
\begin{equation*}
vu(\mu +\rho )-\rho =\pi _{\left( \frak{a}\right) }\left( u(\mu +\rho
)\right) -\rho +\rho _{\frak{a}_{\perp }}+v\left( \pi _{\left( \widetilde{%
\frak{a}_{\perp }}\right) }u(\mu +\rho )-\rho _{\frak{a}_{\perp }}+\rho _{%
\frak{a}_{\perp }}\right) -\rho _{\frak{a}_{\perp }}
\end{equation*}
Use these formulas to decompose the anomalous element $\Psi _{\frak{g}}^{\mu
}$ of the module $L_{\frak{g}}^{\mu }$ into the linear combination of
anomalous elements $\Psi _{\widetilde{\frak{a}_{\perp }}}^{\eta }$ of the
subalgebra $\widetilde{\frak{a}_{\perp }}$-modules $L_{\widetilde{\frak{a}%
_{\perp }}}^{\eta }$:
\begin{equation*}
\begin{array}{l}
\Psi _{\frak{g}}^{\mu }=\sum_{v\in W_{\frak{a}_{\perp }}}\sum_{u\in
U}\epsilon (v)\epsilon (u)e^{vu(\mu +\rho )-\rho }= \\
=\sum_{u\in U}\epsilon (u)e^{\pi _{\frak{a}}\left( u(\mu +\rho )\right)
-\rho +\rho _{\frak{a}_{\perp }}}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
(v)e^{v\left( \pi _{\left( \widetilde{\frak{a}_{\perp }}\right) }u(\mu +\rho
)-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\rho _{\frak{a}%
_{\perp }}}= \\
=\sum_{u\in U}\epsilon (u)e^{\pi _{\frak{a}}\left( u(\mu +\rho )\right) -\pi
_{\frak{h}_{\perp }}\rho -\pi _{\frak{a}}\rho +\mathcal{D}_{\frak{a}_{\perp
}}}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon (v)e^{v\left( \pi _{\left(
\widetilde{\frak{a}_{\perp }}\right) }u(\mu +\rho )-\rho _{\frak{a}_{\perp
}}+\rho _{\frak{a}_{\perp }}\right) -\rho _{\frak{a}_{\perp }}}= \\
=\sum_{u\in U}\epsilon (u)e^{\pi _{\frak{a}}\left[ u(\mu +\rho )-\rho \right]
+\mathcal{D}_{\frak{a}_{\perp }}}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
(v)e^{v\left( \pi _{\left( \widetilde{\frak{a}_{\perp }}\right) }u(\mu +\rho
)-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\pi _{\frak{h}%
_{\perp }}\rho -\rho _{\frak{a}_{\perp }}}= \\
=\sum_{u\in U}\epsilon (u)e^{\pi _{\frak{a}}\left[ u(\mu +\rho )-\rho \right]
+\mathcal{D}_{\frak{a}_{\perp }}}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
(v)e^{v\left( \pi _{\left( \widetilde{\frak{a}_{\perp }}\right) }\left[
u(\mu +\rho )-\rho \right] .-\mathcal{D}_{\frak{a}_{\perp }}+\rho _{\frak{a}%
_{\perp }}\right) -\rho _{\frak{a}_{\perp }}}= \\
=\sum_{u\in U}\;\epsilon (u)e^{\pi _{\left( \frak{a}\right) }\left[ u(\mu
+\rho )-\rho \right] +\mathcal{D}_{\frak{a}_{\perp }}}\Psi _{\widetilde{%
\frak{a}_{\perp }}}^{\pi _{\left( \widetilde{\frak{a}_{\perp }}\right) }%
\left[ u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }}}
\end{array}
\end{equation*}
Dividing both sides by the Weyl element $R_{\frak{a}_{\perp }}=\prod_{\beta
\in \Delta _{\frak{a}_{\perp }}}(1-e^{-\beta })^{\mathrm{mult}(\beta )}$ and
projecting them to the weight space $h_{\frak{a}}^{\ast }$\ we obtain the
desired relation
\begin{eqnarray*}
\pi _{\frak{a}}\left( \frac{\Psi _{\frak{g}}^{\mu }}{R_{\frak{a}_{\perp }}}%
\right)  &=&\sum_{u\in W/W_{\frak{a}_{\perp }}}\;\epsilon (u)e^{\pi _{\frak{a%
}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}_{\perp }}}\pi _{%
\frak{a}}\left( \frac{\Psi _{\widetilde{\frak{a}_{\perp }}}^{\pi _{\left(
\widetilde{\frak{a}_{\perp }}\right) }\left[ u(\mu +\rho )-\rho \right] -%
\mathcal{D}_{\frak{a}_{\perp }}}}{\prod_{\beta \in \Delta _{\frak{a}_{\perp
}}}(1-e^{-\beta })^{\mathrm{mult}(\beta )}}\right)  \\
&=&\sum_{u\in U}\;\epsilon (u)\mathrm{\dim }\left( L_{\widetilde{\frak{a}%
_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) }\right)
e^{\mu _{\frak{a}}\left( u\right) }.
\end{eqnarray*}
\end{proof}
